%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Lead Software Engineer \& DevOps Manager} % Job title
    {Bellese Technologies, LLC} % Organization
    {Remote} % Location
    {2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a team of six engineers to modernize and migrate over 60 apps and 20 databases located in a data center to AWS with zero down time or outages.} 
        \item {Saved over \$410k per year by appropriately sizing each environment and resource, refactoring services to utilize serverless/container based architecture, and implementing time and utilization based auto-scaling rules.}
  \item {Designed CI/CD pipelines to incorporate static and dynamic code scanning, automated builds and releases to various environments, and wrote test suites to validate deployments and availability of services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer} % Job title
    {Passport Labs, Inc.} % Organization
    {Remote} % Location
    {2017 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for the automation, uptime, and scaling of a  global SaaS transportation and mobility platform with over 6 million daily users, serving tens of thousands requests per second multiple times during the day.}
  \item {Implemented cross-regional automated CI/CD pipelines that enabled deployments to lower environments and production multiple times per day.}
  \item {Analyzed and refactored a legacy monolithic code base into numerous individual services. I.e., moved from a classic three tier monolithic app to a modern microservice-based architecture .}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Manager \& Principal Engineer} % Job title
    {CyberSponse, Inc.} % Organization
    {Remote} % Location
    {2016 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Remotely lead and managed two teams: one in Pune, India and one in Dallas, TX. Conducted monthly sprint planning, daily standups, and weekly one-on-one sessions with team members.}
  \item {Implemented build and release pipelines, automated endpoint testing for the application suite and infrastructure, and designed a novel package distribution system for our SaaS platform and on-prem application deployments.}
  \item {Migrated all physical assets to AWS saving \~\$3500 per month with zero downtime or data loss during the migration.}
  \item {Expanded our SaaS platform to include two additional cloud providers and created an on-premise deployment system, enabling additional sales that increased our quarterly reoccurring revenue \~\$7,000.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal DevOps Engineer \& Team Manager} % Job title
    {IBM Watson Health} % Organization
    {Dallas, TX \& Remote} % Location
    {2015 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected CI/CD pipelines that integrated two datacenters and three cloud environments enabling daily deployments to production.}
  \item {Lead a team of four engineers by conducting daily standups, restrospectives, and one-on-one sessions as needed.}
  \item {Responsible for application cloud migrations projected to take twelve months to complete: the task was accomplished over a three month period.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Systems \& DevOps Engineer} % Job title
    {Trinity Industries, Inc.} % Organization
    {Dallas, TX} % Location
    {2014 - 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Saved \~\$25,000 per year by introducing automation, continuous integration, and configuration management to multiple environments.}
  \item {Designed systems of automation for over seven hundred servers that included patching, deployments, self-healing web-services, and compliance reporting.}
  \item {Served as the final escalation point for systems and server related issues.}
      \end{cvitems}
    }

%--------------------------------------------------------
  \cventry
    {Cloud Engineer \& Owner} % Job title
    {Bond Solutions, LLC} % Organization
    {Fayetteville, AR} % Location
    {2010 - 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided business consultation services that included systems engineering, cloud migration \& adoption strategies, and devised automation solutions for a variety of business needs.}
  \item {Clients and customers included established small and medium sized businesses, as well as SaaS/PaaS based startups.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
